\begin{alltt}
================================================================================
Checking IJK and WCF data for well: tw00_00 (row numbering uses 0-indexing)
heel.xyz = 0.00 0.000 1712.0, toe.xyz = 125.0 175.0 1712.0
================================================================================

--------------------------------------------------------------------------------
>>> If any, start removing rows with low WCF for RMS data.
Removing row 1 from RMS data b/c WCF is lower than set tolerance (0.0004 < 0.01)
Removing row 3 from RMS data b/c WCF is lower than set tolerance (0.0003 < 0.01)
Removing row 5 from RMS data b/c WCF is lower than set tolerance (0.0004 < 0.01)
Removing row 7 from RMS data b/c WCF is lower than set tolerance (0.0005 < 0.01)
Removing row 9 from RMS data b/c WCF is lower than set tolerance (0.0032 < 0.01)

--------------------------------------------------------------------------------
>>> If any, start removing rows with low WCF for PCG data. [None removed.]

--------------------------------------------------------------------------------
>>> COMPDAT vectors have different length. Making them equal.
>>> Vector lengths have been made equal: 6 rows were removed from PCG data
b/c IJK values did not match. Rows that were removed: [1 3 8 9 10 11].
WARNING: more than 5 rows removed, check wells are supposed to be equal. 
Continuing comparison.

--------------------------------------------------------------------------------
IJK values are NOT the same for this well.
Testing: IJK (rowwise) >> values differ at the following rows:
row   3:  RMS:  4  4  1 PCG:  3  4  1 DFF:  1  0  0 RMS/PCG:  1  1  1 
row   4:  RMS:  5  5  1 PCG:  3  5  1 DFF:  2  0  0 RMS/PCG:  1  1  1 
row   5:  RMS:  6  6  1 PCG:  4  5  1 DFF:  2  1  0 RMS/PCG:  1  1  1 

Element accuracy: fraction of zero (<tol) elements in diff. column (1=best)
Element accuracy I column: 0.5
Element accuracy J column: 0.833333
Element accuracy K column: 1
Column IJK offset: norm of diff. vector [Euclidean dist.]  (0=best)
Column offset I column:  3
Column offset J column:  1
Column offset K column:  0
Column IJK cosine similarity: angle b/e vectors (1=parallel=best)
Column cosine I column: 0.983495
Column cosine J column: 0.996215
Column cosine K column: 1

--------------------------------------------------------------------------------
WCF values are NOT the same for this well (WCF tol = 0.010).
Testing: WCF (rowwise) >> values differ at the following rows:
row   0:  RMS:   0.604    PCG:   0.524    DFF:   0.080    RMS/PCG:   1.153    
row   1:  RMS:   0.465    PCG:   0.242    DFF:   0.222    RMS/PCG:   1.917    
row   2:  RMS:   0.734    PCG:   0.127    DFF:   0.608    RMS/PCG:   5.787    
row   3:  RMS:   1.110    PCG:   0.582    DFF:   0.528    RMS/PCG:   1.908    
row   4:  RMS:   1.006    PCG:   0.081    DFF:   0.925    RMS/PCG:  12.448    
row   5:  RMS:   4.630    PCG:   0.516    DFF:   4.114    RMS/PCG:   8.975    

Element accuracy: fraction of zero (<tol) elements in diff. column (1=best)
Element accuracy:  0
Column WCF offset: norm of difference vector (0=best)
Column offset:  4.29967
Column WCF cosine similarity: angle b/e vectors (1=parallel=best)
Column cosine measure:  0.745292
\end{alltt}
